Wigglyhedra

### 2024-05-28 draft/wigglyhedra.tex
Updated figure/intro writeup.

\subsection{Curves in a disk and a triangulated category associated to a quiver}
There is an algebraic/categorical model of curves in a disk with marked points, due to Khovanov and Seidel~\cite{kho.sei:02}, which we describe in this section.
This model identifies curves in a disk with objects in a certain triangulated category, and the correspondence has several useful features.
For instance, the number of intersections between two curves is the number of morphisms in the category between the corresponding objects.
Furthermore, the Artin braid group is the fundamental group of the unordered configuration space of points in a disk, and thus acts on the set of curves in the disk.
The associated triangulated category also carries an action by the Artin braid group, and the Khovanov--Seidel map from curves to objects is equivariant with respect to this group action.

We now give a concise account of this correspondence.
We omit the details that do not play a starring role in the remainder of this paper, and direct the reader to the original references.
Recall that the \emph{type \(A_m\)} Dynkin graph is an undirected graph with \(m\) vertices and \(m-1\) edges; each edge connecting successive pairs of points as shown in~\cref{fig:a5-dynkin}.
\begin{figure}[h]
  \centering
  \begin{tikzcd}
    \bullet \arrow[-]{r}& \bullet \arrow[-]{r}& \bullet \arrow[-]{r}& \bullet \arrow[-]{r}& \bullet
  \end{tikzcd}
  \caption{The type \(A_5\) Dynkin graph.}
  \label{fig:a5-dynkin}
\end{figure}
Given an undirected graph as above, we can construct its \emph{doubled quiver}, which is a directed graph in which every undirected edge is replaced by a pair of oppositely oriented arrows, as shown in~\cref{fig:a5-doubled}.
\begin{figure}[h]
  \centering
  \begin{tikzcd}
    \bullet \arrow[bend left]{r}& \bullet \arrow[bend left]{r} \arrow[bend left]{l}& \bullet \arrow[bend left]{r}\arrow[bend left]{l}& \bullet \arrow[bend left]{r}\arrow[bend left]{l}& \bullet \arrow[bend left]{l}
  \end{tikzcd}
  \caption{The doubled quiver of the type \(A_5\) Dynkin graph.}
  \label{fig:a5-doubled}
\end{figure}
The \emph{zig-zag algebra} of the doubled quiver of an undirected graph is a finite-dimensional quotient of the path algebra of the doubled quiver of that graph (see~\cite[Section 3]{hue.kho:01} for the precise definition).

Then there is a triangulated category \(\mathcal{C}_m\) associated to the Dynkin graph of type \(A_m\), constructed as a differential graded version of the homotopy category of projective modules over the zig-zag algebra of the doubled quiver of type \(A_m\).
The precise definition of this category appears in, e.g.,~\cite{sei.tho:01,tho:06} for type \(A_m\) and in~\cite{bap.deo.lic:20} for general undirected graphs.

>>>>

\subsection{Curves in a disk and a triangulated category associated to a quiver}
Curves up to isotopy in a disk with marked points constitute a geometric model of certain objects in a triangulated category.
This correspondence, due to Khovanov--Seidel~\cite{kho.sei:02}, and will enable us to build categorical interpretations of the combinatorial results obtained in this paper.
The aim of this section is to give a concise account of this correspondence and some of its useful features; we refer the reader to~\cite{kho.sei:02} for details.

The triangulated category of interest will be the category \(\mathcal{C}_m = D^b(A_m\text{-mod})\) for a certain finite-dimensional algebra \(A_m\).
The algebra \(A_m\) is defined as the quotient of the path algebra of the quiver with \(m+1\) vertices depicted in~\cref{fig:am-quiver}.
\begin{figure}[h]
  \centering
  \begin{tikzcd}
    0 \arrow[bend left]{r}& 1 \arrow[bend left]{r} \arrow[bend left]{l}& 2 \arrow[bend left]{r}\arrow[bend left]{l}& \cdots \arrow[bend left]{r}\arrow[bend left]{l}& m \arrow[bend left]{l}
  \end{tikzcd}
  \caption{The doubled quiver of the type \(A_5\) Dynkin graph.}
  \label{fig:am-quiver}
\end{figure}

Recall that the type \(A_m\) Dynkin graph is an undirected graph with \(m\) vertices and \(m-1\) edges; each edge connects successive pairs of points as shown in~\cref{fig:a5-dynkin}.
\begin{figure}[h]
  \centering
  \begin{tikzcd}
    \bullet \arrow[-]{r}& \bullet \arrow[-]{r}& \bullet \arrow[-]{r}& \bullet \arrow[-]{r}& \bullet
  \end{tikzcd}
  \caption{The type \(A_5\) Dynkin graph.}
  \label{fig:a5-dynkin}
\end{figure}
Given an undirected graph as above, we can construct its \emph{doubled quiver}, which is a directed graph in which every undirected edge is replaced by a pair of oppositely oriented arrows, as shown in~\cref{fig:a5-doubled}.
\begin{figure}[h]
  \centering
  \begin{tikzcd}
    \bullet \arrow[bend left]{r}& \bullet \arrow[bend left]{r} \arrow[bend left]{l}& \bullet \arrow[bend left]{r}\arrow[bend left]{l}& \bullet \arrow[bend left]{r}\arrow[bend left]{l}& \bullet \arrow[bend left]{l}
  \end{tikzcd}
  \caption{The doubled quiver of the type \(A_5\) Dynkin graph.}
  \label{fig:a5-doubled}
\end{figure}
The \emph{zig-zag algebra} of an undirected graph is a finite-dimensional quotient of the path algebra of the doubled quiver of that graph (see~\cite[Section 3]{hue.kho:01} for the precise definition).

Let \(Z_m\) be the zig-zag algebra of the type \(A_m\) graph.
Let \(\mathcal{C}_m\) be \(K^b(Z-\text{proj})\), which is the bounded homotopy category of graded projective modules over \(Z_m\)
The category \(\mathcal{C}_m\) is triangulated.
The precise definition of this category appears in, e.g.,~\cite{sei.tho:01,tho:06} for type \(A_m\) and in~\cite{bap.deo.lic:20} for general undirected graphs.
